To Do List

### 2021-10-12 inst/manuscript/manuscript.Rmd
reorganized file structure

```{r, results = "hide"}
## GRTS Sample, Design Analysis
data_sf <- sf::st_as_sf(nla_nomiss_both, coords = c("xcoords", "ycoords"),
                        crs = 5070)
library(spsurvey)
grts_samp <- grts(data_sf, n_base = n)
grts_bind <- sprbind(grts_samp)

>>>>

```{r, results = "hide"}
## GRTS Sample, Design Analysis
data_sf <- sf::st_as_sf(nla_nomiss_both, coords = c("xcoords", "ycoords"),
                        crs = 5070)
library(spsurvey)
grts_samp <- grts(data_sf, n_base = n)
grts_bind <- sp_rbind(grts_samp) # Matt you need to install newest version
# devtools::install_github("USEPA/spsurvey", ref = "main")

### 2021-10-12 inst/manuscript/manuscript.tex
reorganized file structure

Though the design-based and model-based approaches apply to statistical
inference in a broad sense, we focus on comparing these approaches for
spatial data. We define spatial data as data that incorporates the
specific locations of the population units into either the design or
estimation process. De Gruijter and Ter Braak (1990) give an early
comparison of design-based and model-based approaches for spatial data,
quashing the belief that design-based approaches could not be used for
spatially correlated data. Thereafter, several comparisons between
design-based and model-based for spatial data have been considered, but
they tend to compare design-based approaches that ignore spatial
locations to model-based approaches (Brus and De Gruijter, 1997; Ver
Hoef, 2002; Ver Hoef, 2008). Cooper (2006) review the two approaches in
an ecological context before introducing a ``model-assisted'' variance
estimator that combines aspects from each approach. In addition to
Cooper (2006), there has been substantial research and development into
estimators that use both design and model-based principles (see e.g.
Cicchitelli and Montanari (2012), Chan-Golston et al. (2020) for a
Bayesian approach, and Sterba (2009)). More recent overviews include
Brus (2020) and Wang et al. (2012), but no numerical comparison has been
made between design-based approaches that incorporate spatial locations
and model-based approaches.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{SpatialDVM_Manuscript_files/figure-latex/fig1-1} \caption{A comparison of sampling under the design-based and model-based frameworks. Points circled are those that are sampled. In the top row, we have one fixed population, and three random samples of n = 4. The response values at each site are fixed, but we obtain different estimates for the mean response because the randomly sampled sites vary from sample to sample. In the bottom row, we have three realizations of the same spatial process sampled at the same locations. The spatial process generating the response values has a single mean, but the realized mean is different in each of the three panels.}\label{fig:fig1}
\end{figure}

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:designanalysis} Types of Sampling Design and
Analysis combinations considered in the simulation study. The columns
give the two types of sampling designs while the rows give the two types
of analyses.}\tabularnewline
\toprule
& IRS & GRTS \\
\midrule
\endfirsthead
\toprule
& IRS & GRTS \\
\midrule
\endhead
Design & IRS-Design & GRTS-Design \\
Model & IRS-Model & GRTS-Model \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\caption{\label{tab:parmtab} Simulation parameters. Total variability
for all scenarios was 2 so that the partial sill was 0, 1, or
1.8.}\tabularnewline
\toprule
& & & \\
\midrule
\endfirsthead
\toprule
& & & \\
\midrule
\endhead
Sample Size (n) & 50 & 100 & 200 \\
Site Locations & Random & Gridded & \\
Partial Sill / Total Variance & 0 & 0.5 & 0.9 \\
Response Type & Normal & Lognormal & \\
\bottomrule
\end{longtable}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{SpatialDVM_Manuscript_files/figure-latex/figeff-1} \caption{Relative Efficiency of the four design-analysis approaches. The plot is faceted by the type of response on the columns and the partial-sill to total-variance ratio on the rows.}\label{fig:figeff}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{SpatialDVM_Manuscript_files/figure-latex/figconf-1} \caption{Coverage of the four design-analysis approaches. All confidence intervals are normal-based and have a nominal confidence level of 0.95, marked with a horizontal line. The plot is faceted by the type of response on the columns and the partial-sill to total-variance ratio on the rows.}\label{fig:figconf}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{SpatialDVM_Manuscript_files/figure-latex/figdata-1} \caption{Population distribution of mercury concentration for 986 lakes in the contiguous United States. Thirty-five lakes were dropped from the analysis because they were missing mercury concentration.}\label{fig:figdata}
\end{figure}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tab:appliedtab} Application of design-based and
model-based approaches to the NLA data set on mercury concentration. The
true mean concentration is 103.2 103.2 ng / g}\tabularnewline
\toprule
Approach & Estimate & SE & 95\% LB & 95\% UB \\
\midrule
\endfirsthead
\toprule
Approach & Estimate & SE & 95\% LB & 95\% UB \\
\midrule
\endhead
IRS-Design & 112.7 & 8.8 & 95.4 & 129.9 \\
IRS-Model & 110.5 & 7.9 & 95.0 & 125.9 \\
GRTS-Design & 101.8 & 6.1 & 89.8 & 113.7 \\
GRTS-Model & 102.3 & 5.9 & 90.8 & 113.9 \\
\bottomrule
\end{longtable}

>>>>

Though the design-based and model-based approaches apply to statistical
inference in a broad sense, we focus on comparing these approaches for
spatial data. We define spatial data as data that incorporates the
specific locations of the population units into either the design or
estimation process. De Gruijter and Ter Braak (1990) give an early
comparison of design-based and model-based approaches for spatial data,
quashing the belief that design-based approaches could not be used for
spatially correlated data. Thereafter, several comparisons between
design-based and model-based for spatial data have been considered, but
they tend to compare design-based approaches that ignore spatial
locations to model-based approaches (Brus and De Gruijter, 1997; Ver
Hoef, 2002, 2008). Cooper (2006) review the two approaches in an
ecological context before introducing a ``model-assisted'' variance
estimator that combines aspects from each approach. In addition to
Cooper (2006), there has been substantial research and development into
estimators that use both design and model-based principles (see
e.g.~Cicchitelli and Montanari (2012), Chan-Golston et al. (2020) for a
Bayesian approach, and Sterba (2009)). More recent overviews include
Brus (2020) and Wang et al. (2012), but no numerical comparison has been
made between design-based approaches that incorporate spatial locations
and model-based approaches.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/fig1-1} \caption{A comparison of sampling under the design-based and model-based frameworks. Points circled are those that are sampled. In the top row, we have one fixed population, and three random samples of n = 4. The response values at each site are fixed, but we obtain different estimates for the mean response because the randomly sampled sites vary from sample to sample. In the bottom row, we have three realizations of the same spatial process sampled at the same locations. The spatial process generating the response values has a single mean, but the realized mean is different in each of the three panels.}\label{fig:fig1}
\end{figure}

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:designanalysis} Types of Sampling Design and
Analysis combinations considered in the simulation study. The columns
give the two types of sampling designs while the rows give the two types
of analyses.}\tabularnewline
\toprule
& IRS & GRTS\tabularnewline
\midrule
\endfirsthead
\toprule
& IRS & GRTS\tabularnewline
\midrule
\endhead
Design & IRS-Design & GRTS-Design\tabularnewline
Model & IRS-Model & GRTS-Model\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}llll@{}}
\caption{\label{tab:parmtab} Simulation parameters. Total variability
for all scenarios was 2 so that the partial sill was 0, 1, or
1.8.}\tabularnewline
\toprule
\endhead
Sample Size (n) & 50 & 100 & 200\tabularnewline
Site Locations & Random & Gridded &\tabularnewline
Partial Sill / Total Variance & 0 & 0.5 & 0.9\tabularnewline
Response Type & Normal & Lognormal &\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figeff-1} \caption{Relative Efficiency of the four design-analysis approaches. The plot is faceted by the type of response on the columns and the partial-sill to total-variance ratio on the rows.}\label{fig:figeff}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figconf-1} \caption{Coverage of the four design-analysis approaches. All confidence intervals are normal-based and have a nominal confidence level of 0.95, marked with a horizontal line. The plot is faceted by the type of response on the columns and the partial-sill to total-variance ratio on the rows.}\label{fig:figconf}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figdata-1} \caption{Population distribution of mercury concentration for 986 lakes in the contiguous United States. Thirty-five lakes were dropped from the analysis because they were missing mercury concentration.}\label{fig:figdata}
\end{figure}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tab:appliedtab} Application of design-based and
model-based approaches to the NLA data set on mercury concentration. The
true mean concentration is 103.2 103.2 ng / g}\tabularnewline
\toprule
Approach & Estimate & SE & 95\% LB & 95\% UB\tabularnewline
\midrule
\endfirsthead
\toprule
Approach & Estimate & SE & 95\% LB & 95\% UB\tabularnewline
\midrule
\endhead
IRS-Design & 112.7 & 8.8 & 95.4 & 129.9\tabularnewline
IRS-Model & 110.5 & 7.9 & 95.0 & 125.9\tabularnewline
GRTS-Design & 101.8 & 6.1 & 89.8 & 113.7\tabularnewline
GRTS-Model & 102.3 & 5.9 & 90.8 & 113.9\tabularnewline
\bottomrule
\end{longtable}

### 2021-10-12 inst/manuscript/notes_to_do.Rmd
reorganized file structure

* put in SRS as base-line sampling setting.
* add FPBK as traditional SRS analysis as methods to analyze SRS sample.
* add FPBK and traditional SRS analysis as additional methods to analyze GRTS sample.
* add GRTS with 10% nugget sites as additional sampling setting? If so, add FPBK to analyze this sample.

>>>>

* put in IRS as base-line sampling setting.
* add FPBK as traditional IRS analysis as methods to analyze SRS sample.
* add FPBK and traditional IRS analysis as additional methods to analyze GRTS sample.
* add GRTS with 10% nugget sites as additional sampling setting? If so, add FPBK to analyze this sample.

* no correlation - normal errors
* strong correlation - normal errors
* no correlation - non-normal errors
* strong correlation - log normal
